### 2020-04-20 final_report/methodology.tex
write supervised learning section

\subsection{Supervised Learning Experiments}
\label{sec:supervised}

\subsubsection{Considered Surrogates}

\begin{table}[h]
	\centering
	\begin{tabular}{llll}
	\toprule
	Surrogate & Acronym & Implementation & Hyperparameters \\
	\midrule
	Support vector machines	& SVM & SciKit Learn & TODO \\
	Gradient boosted trees	& GBT & SciKit Learn & TODO \\
	Extremely random trees	& ERT & SciKit Learn & TODO \\
	AdaBoost	& AB & SciKit Learn & TODO \\
	Gaussian process regression	& GPR & SciKit Learn & TODO \\
	$k$ nearest neighbours	& KNN & SciKit Learn & TODO \\
	Neural networks	& NN & Keras (TensorFlow) & TODO \\
	Inverse distance weighing & IDW & SMT & TODO \\
	Radial basis functions & RBF & SMT & TODO \\
	Stochastic gradient descent & SGD & SciKit Learn & TODO \\
	Ridge regression & RR & SciKit Learn & TODO \\
	Kriging & KRG & SMT & TODO \\
	\bottomrule
	\end{tabular}
	\caption{TODO}
	\label{tbl:surrogates}
\end{table}

TODO: describe classes of surrogates

TODO: reference implementations and original papers

TODO: define NN architectures

@@

	\caption{TODO}
	\label{fig:neural-net-architectures}
\end{figure}

>>>>

\subsection{Evaluation of Supervised Learning Surrogates}
\label{sec:supervised}

In our experiments, we evaluate and compare surrogates in effort to
optimise against metrics described in \cref{sec:metrics}. To attain meaningful
and practically usable results, we require a sufficiently large and diverse pool
of surrogate classes to draw from. This is described by the listing in
\cref{tbl:surrogates}. The presented selection of models includes basic
techniques suitable for linear regression enhanced by the kernel trick or dimension
lifting, methods driven by decision trees, instance-based learning models,
ensemble regressors, randomized algorithms, neural networks and mathematical approaches
developed specifically for the purposes of surrogate modelling. For each of
these classes, a state-of-the-art implementation was selected and adapted to
operate with TBR samples.

\begin{table}[h]
	\centering
	\begin{tabular}{llll}
	\toprule
	Surrogate & Acronym & Implementation & Hyperparameters \\
	\midrule
	Support vector machines	& SVM & SciKit Learn & TODO \\
	Gradient boosted trees	& GBT & SciKit Learn & TODO \\
	Extremely random trees	& ERT & SciKit Learn & TODO \\
	AdaBoost	& AB & SciKit Learn & TODO \\
	Gaussian process regression	& GPR & SciKit Learn & TODO \\
	$k$ nearest neighbours	& KNN & SciKit Learn & TODO \\
	Neural networks	& NN & Keras (TensorFlow) & TODO \\
	Inverse distance weighing & IDW & SMT & TODO \\
	Radial basis functions & RBF & SMT & TODO \\
	Stochastic gradient descent & SGD & SciKit Learn & TODO \\
	Ridge regression & RR & SciKit Learn & TODO \\
	Kriging & KRG & SMT & TODO \\
	\bottomrule
	\end{tabular}
	\caption{Considered surrogate model classes.}
	\label{tbl:surrogates}
\end{table}

In some rows of the table, a single class in reality represents a multitude of
fundamentally similar approaches. Good examples of this are kriging methods and neural
networks. In the case of the former, multiple algorithms such as kriging based on
partial least squares and gradient-enhanced kriging are considered. In the
latter, a host of parametric graphs are defined to realise simplistic network
architecture search (see \cref{fig:nn-archs} for details). Discrimination
between such options is considered an additional hyperparameter of the
corresponding surrogate class.

@@

	\caption{Various considered parametric neural architectures. All layers use ReLU
		activation and random initialisation. Information flow is indicated by
		arrows. Conections between neurons are omitted for clarity.}
	\label{fig:nn-archs}
\end{figure}
